### 2019-02-08 metrics4.tex
metrics

	For women:
	\begin{align*}
	\frac{\Delta ahe}{ahe} \cdot 100\% = 100(\beta_1 + \beta_2)\Delta yrseduc
	\end{align*}
	i.e. the coefficient on $yrseduc$ plus the coefficient on $yrseduc \times female$ times 100 is the percent change of average per hour salary for women adding one additional year of education, holding other things fixed.
	\item 
	\item We should test whether $\beta_2 = 0$ or not. Using coeftest() we can conclude that the null hypothesis can be rejected at the 5\% significance level, i.e. the value of the aditional year of education for men and for women differs.
	\item We need to test the hypothesis that both $\beta_2$ and $\beta_3$ are equal to 0. Using linearhypothesis() we can conclude that the hypothesis should be rejected, i.e. regression lines are different for men and for women.
	\item For men additional year of education increases the average per hour salary by $8.26\%$ for women by $9.9\%$, in statistical terms this is a significant difference (since we reject the hypothesis that $\beta_2 = 0$) in real world sense I think not.
\end{enumerate}
\section*{Problem 6}

\end{document}

>>>>

	For women:
	\begin{align*}
	\frac{\Delta ahe}{ahe} \cdot 100\% = 100(\beta_1 + \beta_2)\Delta yrseduc
	\end{align*}
	i.e. the coefficient on $yrseduc$ plus the coefficient on $yrseduc \times female$ times 100 is the percent change of average per hour salary for women adding one additional year of education, holding other things fixed.
	\item 
	\item We should test whether $\beta_2 = 0$ or not. Using coeftest() we can conclude that the null hypothesis can be rejected at the 5\% significance level, i.e. the value of the aditional year of education for men and for women differs.
	\item We need to test the hypothesis that both $\beta_2$ and $\beta_3$ are equal to 0. Using linearhypothesis() we can conclude that the hypothesis should be rejected, i.e. regression lines are different for men and for women.
	\item For men additional year of education increases the average per hour salary by $8.26\%$ for women by $9.9\%$, in statistical terms this is a significant difference (since we reject the hypothesis that $\beta_2 = 0$) in real world sense I think not.
\end{enumerate}
\section*{Problem 6}
Nothing changed. R did not include $male \times yrseduc$ in regression because $male \times yrseduc = yrseduc - female \times yrseduc$ i.e. regressors are perfectly linearly dependent.
\section*{Problem 7}
Summary for two models are depicted on the Fig. \ref{fig2} and \ref{fig3} respectively.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{age_cub}
	\caption{Summary of regression}\label{fig2}
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{age_cub2}
	\caption{Summary of regression}\label{fig3}
\end{figure}
\begin{enumerate}[a.]
	\item Denote the coefficients of the models as follows:
	\begin{align*}
	\ln ahe = \beta_0 + \beta_1 female + \beta_2 yrseduc + \beta_3 age + \beta_4 age^2 + \beta_5 age^3 + \beta_6 female \times yrseduc + \\
	+\beta_7 female \times age + \beta_8 female \times age^2 + \beta_9 female \times age^3
	\end{align*}
	For men :
	\begin{align*}
	\text{1st model: } 100 \beta_2 = 8.08\\
	\text{2nd model: } 100 \beta_2 = 8.03\\
	\end{align*}
	i.e. interaction terms do not significantly affect the value of additional year of education for men, in a real-world sense.
	For women:
	\begin{align*}
	\text{1st model: } 100(\beta_2 + \beta_6) = 10.13\\
	\text{2nd model: } 100(\beta_2 + \beta_6) = 10.07
	\end{align*}
	i.e. interaction terms do not significantly affect the value of additional year of education for women, in a real-world sense, either.
	\item \begin{align*}
	\frac{\Delta ahe}{ahe} \cdot 100 = 100(\beta_1 + 16 \beta_6 + 25 \beta_7 + 25^2 \beta_8 + 25^3 \beta_9)\Delta female = -8.42 \Delta female
	\end{align*}
	i.e. on average 25-year old female workers with 16 years of education earn by 8.4\% less than their male counterparts.
	\item \begin{align*}
	\frac{\Delta ahe}{ahe} \cdot 100 = 100(\beta_1 + 16 \beta_6 + 55 \beta_7 + 55^2 \beta_8 + 55^3 \beta_9)\Delta female = -22.69 \Delta female
	\end{align*}
	i.e. on average 55-year old female workers with 16 years of education earn by 22.7\% less than their male counterparts.
	\item We need to test the hypothesis that $\beta_7 = \beta_8 = \beta_9 = 0$. Using linearHypothesis() we can conclude that at the 5\% significance level the hypothesis should be rejected. That is, a gender gap depends on age.
	\item Yes, there is evidence. Coefficients jointly significanly differ from zero and moreover based on (c) and (d) we can conclude that for 25 year-old female and for 55-year old the gender gap significantly differs in a real-world terms (8\% for the former and 22.7\% for the latter)
\end{enumerate}
\end{document}
